Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
some fixes to introduction
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60897 72bbbca6-d526-0410-a7d9-f06f51895060

This article describes work towards the development of a dependency treebank for Kazakh, a Turkic language spoken in Central Asia and Europe.
Despite its status as a \emph{core} Turkic
language, little computational-linguistic research has been published on syntactic
parsing for Kazakh.
A valuable resource in the study of syntactic parsing is
a treebank---a corpus of parsed text containing gold-standard syntactic annotation.

Freely available treebanks exist for many languages, such as large languages like Finnish \parencite{haverinen2013tdt,voutilainen11} 
and Polish (xxx) and smaller languages like Irish \parencite{Lynn12}. To our knowledge only one treebank
exists for another language, Turkish \parencite{Oflazer03}, which is unfortunately not freely available.

@@

The remainder of the paper is organised as follows. Section~\ref{sec:back} gives some
background linguistic information on Kazakh, and outlines some special challenges in
parsing Kazakh. In Section~\ref{sec:method} we describe the corpus itself and methodology
used in annotating it. Section~\ref{sec:annotation} gives a sketch of some decisions
we have made with respect to annotation guidelines, referring back to the discussion in
Section~\ref{sec:back}. For reasons of space, these guidelines are not complete, but
present a subset of guidelines which are of particular interest. A small experiment
in statistical dependency parsing using the corpus is presented in Section~\ref{sec:eval},
and in Sections~\ref{sec:future} and \ref{sec:conclusions} we give perspectives
for future work and some concluding remarks.

@@

\section{Background}

@@

\section{Methodology}

@@

\section{Evaluation}

@@

\section{Future work}

>>>>

This article describes work towards the development of a dependency treebank for Kazakh, a Turkic language spoken in Central Asia and Europe.
Despite its status as a \emph{core}\footnote{FIXME} Turkic %FIXME
language, little computational-linguistic research has been published on syntactic
parsing for Kazakh.
A valuable resource in the study of syntactic parsing is
a treebank---a corpus of parsed text containing gold-standard syntactic annotation.

Freely available treebanks exist for many languages, such as large languages like Finnish \parencite{haverinen2013tdt,voutilainen11} 
and Polish (xxx) and smaller languages like Irish \parencite{Lynn12}. To our knowledge, however, a treebank exists for only one other Turkic language, Turkish \parencite{Oflazer03}, which is unfortunately not freely available.

@@

The remainder of the paper is organised as follows. Section~\ref{sec:back} gives some
background linguistic information on Kazakh, and outlines some special challenges in
parsing Kazakh. In Section~\ref{sec:method} we describe the corpus that we annotated and the methodology
used in annotating it. Section~\ref{sec:annotation} gives a sketch of some decisions
we have made with respect to annotation guidelines, referring back to the discussion in
Section~\ref{sec:back}. For reasons of space, these guidelines are not complete, but
present a subset of guidelines which are of particular interest. A small experiment
in statistical dependency parsing using the corpus is presented in Section~\ref{sec:eval},
and in Sections~\ref{sec:future} and \ref{sec:conclusions} we give perspectives
for future work and some concluding remarks.

@@

\section{Background}\label{sec:back}

@@

\section{Methodology}\label{sec:method}

@@

\section{Evaluation}\label{sec:eval}

@@

\section{Future work}\label{sec:future}
